---
title: "Pstat131HW1"
author: "Wentao Yu"
date: '2022-09-23'
output:
  html_document:
    df_print: paged
---
Question1:
The supervised learning is using the labeled data sets, which the unsupervised learning is using algorithm to clustering and analyze the unlabeled data sets. The main difference is the use of labeled data sets. (Need revise)

Question2:
Question3:
Question4:
Question5:
Question6:

```{r include=FALSE}
#install.packages("tidyverse")
#install.packages("corrplot")
#install.packages('ggthemes')
library(tidyverse)
library(corrplot)
library(ggthemes)
```
Exercise1:
```{r}
ggplot(mpg,aes(hwy))+geom_histogram(color = "white", binwidth = 1)
```
Explanation:

Exercise2:
```{r}
ggplot(mpg,aes(hwy,cty))+geom_point()
```
Explanation:

Exercise3:
```{r}
ggplot(mpg,aes(x = reorder(manufacturer,manufacturer, function(x)-length(x))))+geom_bar()+coord_flip()+
  labs(x = 'manufacturer', y = 'counts')
# how to change it to from highest to lowest
```
Explanation: Dodge produces the most cars, and Lincoln produces the least cars. 

Exercise4:
```{r}
ggplot(mpg,aes(hwy)) + geom_boxplot(aes(group=cyl))
```
Explanation:

Exercise5:
```{r}
numeric_data <- select_if(mpg, is.numeric)
corrplot(cor(numeric_data),method = 'number', type = 'lower')
```
Explanation: hwy and cty have positive correlation. cyl and displ have positive correlation. cty has negative correlations with both displ and cyl. hwy has negative correlations with both displ and cyl. 

Exercise 6: 
```{r vehicle vs hwy boxplot}
ggplot(mpg, aes(x = hwy, y= class))+
  geom_boxplot(color = 'black')+
  geom_point(position = 'jitter', color = 'light gray')+
  theme_bw()+
  labs(x='Highway MPG', y='Vehicle Class')
```









