---
title: "Final Project"
author: "Wentao Yu"
date: "2022-10-01"
output: html_document
---

```{r include=FALSE}
#install.packages("readxl")
#install.packages('xts')
library(xts)
#library(readxl)
#data <- read_excel("/Users/wentaoyu/Documents/UCSB File/Stats/Pstat131/Pstat131/TSLA.xlsx")
#install.packages("quantmod")
library(quantmod)
```
```{r dataset}
start_date <- as.Date("2018-07-01")
end_date <- as.Date("2022-09-30")
TSLAData <- getSymbols('TSLA', from = start_date, to = end_date, auto.assign = F)
TSLAData
```
##### An overview of dataset
The data set contains the open price, close price, highest price, lowerst price, volumn, and adjusted. 
I get the data from historical Tesla stock data from yahoo. 
I can separate the data set into 95% of the data be observations, and left 5% be predictor.
I am working on the numeric data. 
There is no missing data, and I have no idea how to do with my data. 

##### An overview of my research question
I am interested in predicting price of Tesla stock. 

##### Proposed project timeline

##### Questions or conserns
