---
title: "Final Project"
author: "Wentao Yu"
date: "2022-10-01"
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: show
---
## Introduction
Predict the potability of water with other 9 variables.
This project aims to find the relationship between the potability if water is safe for human to consume with other 9 variables containing:\
1. PH value\
2. Hardness\
3. Solids(Total dissolved solids - TDS)\
4. Chloramines\
5. Sulfate\
6. Conductivity\
7. Organic_carbon\
8. Trihalomethanes\
9. Turbidity

## R packages loading
```{r include=FALSE}
library(xgboost)
library(vip)
library(ranger)
library(rpart.plot)
library(corrplot)
library(tidymodels)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(corrr)
library(discrim)
library(poissonreg)
library(klaR)
library(pROC)
library(janitor)
library(glmnet)
library(ISLR)
library(ISLR2)
tidymodels_prefer()
```

## Data Cleaning
```{r}
waterdata <- read.csv('/Users/wentaoyu/Documents/UCSB File/Stats/Pstat131/Pstat131/Final Project/water_potability.csv')
waterdata <- clean_names(waterdata)
dim(waterdata)
```













